Precise Weed and Maize classification through Convolutional Neuronal Networks

### 2017-07-21 PaperBCJ.tex
nueva conclusion
nueva conclusion

\begin{table}[h!]
\centering
\begin{tabular}[c c c c]{|p{1.1 cm}|p{1.7cm}|p{1.7cm}|p{2.0cm}|} 
 \hline
 \textbf{Parameter} &\textbf{GPU(Without Threading) } & \textbf{CPU with Threading} & \textbf{RaspBerry Pi 3 with Threading} \\ 
 \hline 
 Time(s) & 0.0171 & 0.196 & 7.714  \\ [0.95ex]
 \hline
 FPS & 58.47  & 5.08 & 0.36  \\ [0.95ex]
 \hline
\end{tabular}
\caption{Test of a complete image and the frames per second}
\label{table:5}
\end{table}

@@

>>>>

\begin{table}[h!]
\centering
\begin{tabular}[c c c c]{|p{1.1 cm}|p{1.7cm}|p{1.7cm}|p{2.0cm}|} 
 \hline
 \textbf{Parameter} &\textbf{GPU(Without Threading) } & \textbf{CPU with Threading} & \textbf{RaspBerry Pi 3 with Threading} \\ 
 \hline 
 Time(s) & 0.0171 & 0.196 & 2.714  \\ [0.95ex]
 \hline
 FPS & 58.47  & 5.08 & 0.36  \\ [0.95ex]
 \hline
\end{tabular}
\caption{Test of a complete image and the frames per second}
\label{table:5}
\end{table}

@@

\begin{comment}	
En el caso de querer implementar el algoritmo en un sitema embedded, no se recomienda trabajar con procesador como el de la Rasp Berry Pi 3, pues tiene  un procesamiento muy lento debido a que los frames por segundo necesario para analizar las imagenes es significativamente bajo, por lo que se debera elegir una targeta que disponga de GPU, sin necesidad del uso de Multithreading y Batching. 
\end{comment}

In the case of wanting to implement the algorithm in an embedded system, it is not recommended to work with a processor like Rasp Berry Pi 3, because it has a very slow processing because the frames per second needed to analyze the images is significantly low, So you should choose a card that has GPU, without the need for Multithreading and Batching. \\
